---
format: html
echo: false
warning: false
footer-left: "Made with [surveydown](https://surveydown.org)"
footer-right: '[<i class="bi bi-github"></i> Source Code](https://github.com/surveydown-dev/demos)'
---

```{r}
library(surveydown)
```

::: {.sd_page id=welcome}

# Demo - Reactive Question

Hi! This is a showcase of a reactive question that surveydown supports.

The second question is hidden by default. It will be shown as long as the first question is answered. It's question label and options will dynamically change based on the choice of the first question.

This is done by defining a question in the `server()` function in `app.R`, and call it using `sd_output()` in `survey.qmd`.

```{r}
sd_question(
  id     = "pet_type",
  type   = "mc",
  label  = "Which do you like more, dogs or cats?",
  option = c("Dogs" = "dog", "Cats" = "cat")
)

sd_output(id = "pet_owner", type = "question")

sd_next()
```

:::

::: {.sd_page id=end}

## End

This is the end of the demo survey showcasing the **reactive question**.

```{r}
sd_close()
```

:::
