---
format: html
echo: false
warning: false
footer-left: "Made with [surveydown](https://surveydown.org)"
footer-right: '[<i class="bi bi-github"></i> Source Code](https://github.com/surveydown-dev/templates)'
---

```{r}
library(surveydown)
```

::: {.sd_page id=welcome}

# Template - Reactive Questions

There are 2 questions in this survey. The first question is static. The second question is reactive, hidden by default, and will be shown as long as the first question is answered. Its question label and options will dynamically change based on the choice of the first question.

This is done by defining a question in the `server()` function in `app.R`, and call it using `sd_output()` in `survey.qmd`.

```{r}
sd_question(
  id     = "pet_type",
  type   = "mc",
  label  = "Which do you like more, dogs or cats?",
  option = c("Dogs" = "dog", "Cats" = "cat")
)

sd_output(id = "pet_owner", type = "question")

sd_next()
```

:::

::: {.sd_page id=end}

## End

This is the end of the survey template of reactive questions.

```{r}
sd_close()
```

:::
