---
format: html
echo: false
warning: false
footer-left: "Made with [surveydown](https://surveydown.org)"
footer-right: '[<i class="bi bi-github"></i> Source Code](https://github.com/surveydown-dev/demos)'
---

```{r}
library(surveydown)
```

::: {#welcome .sd-page}

# Demo - Conditional Display

Hi! This is a showcase of the "conditional display" feature that surveydown supports.

It consists of:

1. Simple conditional display
2. Complex conditional display
3. Conditional display based on a numeric value
4. Conditional display based on multiple inputs

Please proceed to the next page.

```{r}
sd_next()
```

:::

::: {#basic_showif .sd-page}

## 1. Simple conditional display

If the "**Other**" option is chosen, a question asking the other penguin type will appear.

This is done by using the `sd_show_if()` function in the `server` of `app.R`.

```{r}
sd_question(
  type  = 'mc',
  id    = 'penguins_simple',
  label = "Which is your favorite type of penguin?",
  option = c(
    'Adélie'    = 'adelie',
    'Chinstrap' = 'chinstrap',
    'Gentoo'    = 'gentoo',
    'Other'     = 'other'
  )
)

sd_question(
  type  = "text",
  id    = "penguins_simple_other",
  label = "Please specify the other penguin type:"
)

sd_next()
```

:::

::: {#custom_showif .sd-page}

## 2. Complex conditional display

Say that we want to have a more complicated `show_if` condition. Now there are 2 questions. Only if the user chooses both "**Other**" and "**Show**" will the other penguin question appear. This is also done by using the `sd_show_if()` function in the `server` of `app.R`.

```{r}
sd_question(
  type  = 'mc',
  id    = 'penguins_complex',
  label = "Which is your favorite type of penguin?",
  option = c(
    'Adélie'    = 'adelie',
    'Chinstrap' = 'chinstrap',
    'Gentoo'    = 'gentoo',
    'Other'     = 'other'
  )
)

sd_question(
  type  = 'mc',
  id    = 'show_other',
  label = "Should we show the 'other' option question?",
  option = c(
    'Show' = 'show',
    'Hide' = 'hide'
  )
)

sd_question(
  type  = "text",
  id    = "penguins_complex_other",
  label = "Please specify the other penguin type:"
)

sd_next()
```

:::

::: {#numeric_show_if .sd-page}

## 3. Conditional display based on a numeric value

Sometimes you may want to display a question based on a user input value. In the question below, if you type in a value greater than **1**, you'll see the conditional question.

::: {.callout-note}
In surveydown, all input values are stored as string. In the `sd_show_if()` function, use `as.numeric()` to wrap your input in order to change the data type into numeric.
:::

```{r}
sd_question(
  type  = "numeric",
  id    = "car_number",
  label = "How many cars do you have in your household?"
)

sd_question(
  type   = "mc",
  id     = "ev_ownership",
  label  = "Is your backup car a gasoline car or an EV?",
  option = c(
    "Gasoline" = "gasoline",
    "EV"  = "ev"
  )
)

sd_next()
```

:::

::: {#multi_show_if .sd-page}

## 4. Conditional display based on multiple inputs

In other cases, you might display a question based on multiple user input values. The conditions are explained below:

1. If you pick either Apple or Banana, you'll be popped with a question asking how many apples/bananas do you eat per day.
2. If you pick more than 3 types, you'll be popped with a question as well.

```{r}
sd_question(
  type  = "mc_multiple_buttons",
  id    = "fav_fruits",
  label = "Pick your favorite fruit(s):",
  option = c(
    "Apple"  = "apple",
    "Banana" = "banana",
    "Peach"  = "peach",
    "Orange" = "orange",
    "Grape"  = "grape"
  )
)

sd_question(
  type   = "mc_buttons",
  id     = "apple_or_banana",
  label  = glue::glue("How many {sd_output('fav_fruits', type = 'value')}(s) do you eat in a day?"),
  option = seq(1,5)
)

sd_question(
  type   = "mc_buttons",
  id     = "fruit_number",
  label  = "You picked a lot of fruit types. How many do you eat in a day?",
  option = seq(1,5)
)

sd_next()
```

:::

::: {#end .sd-page}

## This is the end of the demo survey showcasing the conditional display feature.

```{r}
sd_close()
```

:::
