---
# General Settings
format: html
echo: false
warning: false

# Theme Settings
theme: default
barposition: top
footer-left: "Made with [surveydown](https://surveydown.org)"
footer-right: '[<i class="bi bi-github"></i> Source Code](https://github.com/surveydown-dev/templates)'

# Survey Settings
use-cookies: false
auto-scroll: false
rate-survey: false
system-language: en
highlight-unanswered: true
highlight-color: blue
capture-metadata: true
all-questions-required: false
required-questions:
  - screening_question
---

```{r}
library(surveydown)
```

::: {.sd_page id=welcome}

# Template - External Redirect

::: {.callout-important}

To properly showcase this survey, add this to your URL and press enter:

```{r}
#| echo: true
#| eval: false

/?id_a=a123&id_b=b234&id_c=c345
```

For example, if your original URL is:

`http://my.url`

Then your new URL should be:

`http://my.url/?id_a=a123&id_b=b234&id_c=c345`

:::

::: {.callout-tip}

1.  A **static** button is defined in `survey.qmd`. It provides a static, hard-coded target URL.
2.  A **reactive** button is defined in the `server` part of `app.R`. It grabs parameters from the URL and allows you to use them to construct a new redirect URL.

:::

In this survey, we showcase both the static and reactive redirections.

```{r}
sd_question(
  type  = "mc",
  id    = "screening_question",
  label = "**Which page do you want to go to?**",
  option = c(
    "Normal ending with static redirect button"      = "normal_end_1",
    "Normal ending with reactive redirect button"    = "normal_end_2",
    "Screenout ending with reactive redirect button" = "screenout"
  )
)

sd_next()
```

:::

::: {.sd_page id=end_page_1}

## This it the normal ending page with static redirect buttons.

This is a static redirect button to Google.

```{r}
# Static redirect
sd_redirect(
  id     = "redirect",
  url    = "https://www.google.com",
  label  = "Click to Google",
  button = TRUE
)
```

This is a static redirect button with a count-down.

```{r}
# Static redirect with countdown delay
sd_redirect(
  id     = "redirect_countdown",
  url    = "https://www.google.com",
  label  = "Click to Google or Wait for 10 Seconds",
  button = TRUE,
  delay  = 10
)
```

:::

::: {.sd_page id=end_page_2}

## This it the normal ending page with reactive redirect button.

This is a reactive redirect button that contains a customized redirect url, including url parameters and an indicator of `status=0`.

```{r}
sd_output("redirect_normal")
```

:::

::: {.sd_page id=screenout_page}

## This it the screenout page with reactive redirect button.

This is a reactive redirect button that contains a customized redirect url, including url parameters and an indicator of `status=1`.

```{r}
sd_output("redirect_screenout")
```

:::
