---
format: html
echo: false
warning: false
footer-left: "Made with [surveydown](https://surveydown.org)"
footer-right: '[<i class="bi bi-github"></i> Source Code](https://github.com/surveydown-dev/demos)'
---

```{r}
library(surveydown)
```

::: {#welcome .sd-page}

# Demo - Conditional Skip

Hi! This is a showcase of the conditional skipping feature that surveydown supports.

It consists of:

1. Simple skipping
2. Complex skipping

Please proceed to the next page.

```{r}
sd_next()
```

:::

::: {#basic_skipping .sd-page}

## 1. Simple skipping
 
If the "**No**" option is chosen, you will be sent to the screenout page.

This is done by using the `sd_skip_if()` function in the `server` of `app.R`.

```{r}
sd_question(
  type  = 'mc',
  id    = 'vehicle_simple',
  label = "Do you own your vehicle?",
  option = c(
    'Yes' = 'yes',
    'No'  = 'no'
  )
)

sd_next()
```

:::

::: {#custom_skipping .sd-page}

## 2. Complex skipping
 
Say that we want to have a more complicated condition for screening out respondents. Now there are 2 questions. If the user chooses "**No**" for both questions, they'll be sent to the screenout page. This is also done by using the `sd_skip_if()` function in the `server` of `app.R`.

```{r}
sd_question(
  type  = 'mc',
  id    = 'vehicle_complex',
  label = "Do you own your vehicle?",
  option = c(
    'Yes' = 'yes',
    'No'  = 'no'
  )
)

sd_question(
  type  = 'mc',
  id    = 'buy_vehicle',
  label = "Are you looking to buy a vehicle soon?",
  option = c(
    'Yes' = 'yes',
    'No'  = 'no'
  )
)

sd_next()
```

:::

::: {#end .sd-page}

## End page

This is the normal end page for respondents who **do not** get screened out.

```{r}
sd_close()
```

:::

::: {#screenout .sd-page}

## Screenout page

This is the **screenout page** for respondents who were sent to the screenout page.

```{r}
sd_close()
```

:::
