---
format: html
echo: false
warning: false
---

```{r}
library(surveydown)
```

::: {#basic_skipping .sd-page}

# Demo survey of the `skip_if` feature

::: {.callout-note}

This is a demo survey showcasing the functionality of <a href="https://surveydown.org" target="_blank">surveydown</a>. It doesn't collect any data.

This demo utilizes cookies (stored in your browser). Use incognito mode for a fresh start.

The GitHub repo of all demos can be accessed <a href="https://github.com/surveydown-dev/demos" target="_blank">here</a>.

:::

## Simple Skipping
 
If the "**No**" option is chosen, you will be sent to the screenout page.

This is done by using the `sd_skip_if()` function in the `server` of `app.R`.

```{r}
sd_question(
  type  = 'mc',
  id    = 'vehicle_simple',
  label = "Do you own your vehicle?",
  option = c(
    'Yes' = 'yes',
    'No'  = 'no'
  )
)

sd_next()
```

:::

::: {#custom_skipping .sd-page}

## Complex Skipping
 
Say that we want to have a more complicated condition for screening out respondents. Now there are 2 questions. If the user chooses "**No**" for both questions, they'll be sent to the screenout page. This is also done by using the `sd_skip_if()` function in the `server` of `app.R`.

```{r}
sd_question(
  type  = 'mc',
  id    = 'vehicle_complex',
  label = "Do you own your vehicle?",
  option = c(
    'Yes' = 'yes',
    'No'  = 'no'
  )
)

sd_question(
  type  = 'mc',
  id    = 'buy_vehicle',
  label = "Are you looking to buy a vehicle soon?",
  option = c(
    'Yes' = 'yes',
    'No'  = 'no'
  )
)

sd_next()
```

:::

::: {#end .sd-page}

## End page

This is the normal end page for respondents who **do not** get screened out.

```{r}
sd_close()
```

:::

::: {#screenout .sd-page}

## Screenout page

This is the **screenout page** for respondents who were sent to the screenout page.

```{r}
sd_close()
```

:::
