---
format: html
echo: false
warning: false
footer-left: "Made with [surveydown](https://surveydown.org)"
footer-right: '[<i class="bi bi-github"></i> Source Code](https://github.com/surveydown-dev/templates)'
---

```{r}
library(surveydown)
```

::: {.sd_page id=welcome}

# Template - Questions Defined with YAML

This is a showcase of defining questions with a `questions.yml` file.

The `sd_question()` allows a `yml` argument default to `"questions.yml"`. If you have such file in your project root folder, you can use it to support your question definition.

You can also change to other file name or directory and define questions like this:

```{r}
#| eval: false
#| echo: true
sd_question(
  id = "your_question_id",
  yml = "folder_name/file_name.yml"
)
```

Please click on the "Next" button to see the demo questions.

```{r}
sd_next()
```

:::

::: {.sd_page id=question_types}

# Question types

This page showcases the different types of question supported by `{surveydown}`. They are all defined in `"questions.yml"` and called by `sd_question(id = "question_id")`.

The question types are:

  - `text`: Single line open text input.
  - `textarea`: Multiple line open text input.
  - `numeric`: Single line numeric text input.
  - `mc`: Multiple choice with a single select option (radio buttons).
  - `mc_buttons`: Same as `mc` but as a "button" style instead of radio buttons.
  - `mc_multiple`: Multiple choice with mutliple select options (check boxes).
  - `mc_multiple_buttons`: Same as `mc_multiple` but as a "button" style instead of check boxes.
  - `select`: Select a choice from a dropdown menu.
  - `slider`: Slider to select discrete categories or continuous numbers.
  - `date`: Select a date from a calendar widget.
  - `daterange`: Select two dates from calendar widgets (e.g. begin and end dates).
  - `matrix`: Several questions with same list of options. Each question is in fact an `mc` question.

#### Use `type = 'text'` to specify a text input type question:

```{r}
sd_question("silly_word")
```

#### Use `type = 'textarea'` to specify a textarea input type question:

```{r}
sd_question("silly_paragraph")
```

#### Use `type = 'numeric'` to specify a numeric input type:

```{r}
sd_question("age")
```

#### Use `type = 'mc'` to specify a multiple choice type question with a single choice option:

```{r}
sd_question("artist")
```

#### Use `type = 'mc_buttons'` to generate the button version of `mc`:

```{r}
sd_question("fruit")
```

#### Use `type = 'mc_multiple'` to specify a multiple choice type question with multiple selection enabled:

```{r}
sd_question("swift")
```

#### Use `type = 'mc_multiple_buttons'` to generate the button version of `mc_multiple`:

```{r}
sd_question("michael_jackson")
```

#### Use `type = 'select'` to specify a drop down select type question:

```{r}
sd_question("education")
```

#### Use `type = 'slider'` to specify a slider input type:

```{r}
sd_question("climate_care")
```

#### Use `type = 'slider_numeric'` to specify a numeric slider input type:

```{r}
sd_question("slider_single_val")
```

#### `type = 'slider_numeric'` can also be used for range selection (2 numerics):

```{r}
sd_question("slider_range")
```

#### Use `type = 'date'` to specify a date input type:

```{r}
sd_question("dob")
```

#### Use `type = 'daterange'` to specify a daterange input type:

```{r}
sd_question("hs_date")
```

#### Use `type = 'matrix'` to specify a matrix input type:

```{r}
sd_question("car_preference")
```

```{r}
sd_next()
```

:::

::: {.sd_page id=end}

## Thanks for taking our survey!

```{r}
sd_close()
```

:::
