---
format: html
echo: false
warning: false
---

```{r}
library(surveydown)
```

::: {#welcome .sd-page}

# Demo survey of external redirects

::: {.callout-note}

This is a demo survey showcasing the functionality of <a href="https://surveydown.org" target="_blank">surveydown</a>. It doesn't collect any data.

This demo utilizes cookies (stored in your browser). Use incognito mode for a fresh start.

The GitHub repo of all demos can be accessed <a href="https://github.com/surveydown-dev/demos" target="_blank">here</a>.

:::

::: {.callout-important}

To properly showcase this demo, add this to your URL and press enter:

```{r}
#| echo: true
#| eval: false

/?id_a=a123&id_b=b234&id_c=c345
```

For example, if your original URL is:

`http://my.url`

Then your new URL should be:

`http://my.url/?id_a=a123&id_b=b234&id_c=c345`

:::

::: {.callout-tip}

1.  A **static** button is defined in `survey.qmd`. It provides a static, hard-coded target URL.
2.  A **reactive** button is defined in the `server` part of `app.R`. It grabs parameters from the URL and allows you to use them to construct a new redirect URL.

:::

In this demo, we showcase both the static and reactive redirections.

```{r}
sd_question(
  type  = "mc",
  id    = "screening_question",
  label = "**Which page do you want to go to?**",
  option = c(
    "Normal ending with static redirect button"      = "normal_end_1",
    "Normal ending with reactive redirect button"    = "normal_end_2",
    "Screenout ending with reactive redirect button" = "screenout"
  )
)

sd_next()
```

:::

::: {#end_page_1 .sd-page}

## This it the normal ending page with static redirect buttons.

This is a static redirect button to Google.

```{r}
# Static redirect
sd_redirect(
  id     = "redirect",
  url    = "https://www.google.com",
  label  = "Click to Google",
  button = TRUE
)
```

This is a static redirect button with a count-down.

```{r}
# Static redirect with countdown delay
sd_redirect(
  id     = "redirect_countdown",
  url    = "https://www.google.com",
  label  = "Click to Google or Wait for 10 Seconds",
  button = TRUE,
  delay  = 10
)
```

:::

::: {#end_page_2 .sd-page}

## This it the normal ending page with reactive redirect button.

This is a reactive redirect button that contains a customized redirect url, including url parameters and an indicator of `status=0`.

```{r}
sd_output("redirect_normal")
```

:::

::: {#screenout_page .sd-page}

## This it the screenout page with reactive redirect button.

This is a reactive redirect button that contains a customized redirect url, including url parameters and an indicator of `status=1`.

```{r}
sd_output("redirect_screenout")
```

:::
