---
format: html
echo: false
warning: false
footer-left: "Made with [surveydown](https://surveydown.org)"
footer-right: '[<i class="bi bi-github"></i> Source Code](https://github.com/surveydown-dev/demos)'
---

```{r}
library(surveydown)
```

::: {.sd_page id=vehicle}

# Demo - drilldown

::: {.callout-note}

The name of `drilldown` mimics the package name `surveydown`. It means the latter question options are defined from the former selection. It's like "drilling" down from a higher level.

This is a demo of car selection. The **Model** options will change based on the selection of **Make**. By doing this, you'll only see the Models belonging the correct Makes.

:::

Tell us about your vehicle:

```{r}
years <- rev(seq(2010, 2025, 1))
names(years) <- years

sd_question(
  type   = "select",
  id     = "year",
  label  = "Model Year:",
  option = years
)

sd_output('make', type = 'question')

sd_output('model', type = 'question')

sd_next()
```

:::

::: {.sd_page id=end}

```{r}
sd_close()
```

:::
